---
title: "Reproducible Research: Peer Assessment 1"
output:html_document
---

Please refer to the readme document in this repository for details on the 
assignment. 

## Loading and preprocessing the data

I load the data in raw and then ensure the dates are in the right format and 
the time intervals are factors for ease of analysis.

```{r}

## Load in the necessary libraries
library(dplyr)
library(ggplot2)
library(lubridate)

## Unzipping file and reading into r
unzip("activity.zip")
activity <- read.csv("activity.csv", stingsAsFactors = FALSE)

## Formatting dates and turning day intervals into factors
activity$date <- ymd(activity$date)
activity$interval <- as.factor(activity$interval)

```

## What is mean total number of steps taken per day?

```{r}
## Create a summary of the data summing steps by day

datesum <- summarize(group_by(activity, date), sum(steps, na.rm = TRUE))
names(datesum)[2] <- "steps"

## Plot the histogram of total steps per day
qplot(date, steps, data = datesum, geom = "histogram", stat = "identity", main = "Total Number of Steps per Day")

## Calculate mean and median of the steps taken per day
meansteps <- mean(datesum$steps)
mediansteps <- median(datesum$steps)

```


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
